Market Simulator

### 2020-08-13 analysis/05_market_simulator.Rmd
started builing the persona reactive element. Need to change the input_ids in the selectInputs to match

df <- reactive({
  #Amnesty International
    beta$ai_value <- 0
    beta$ai_value[beta$levels == 'Amnesty International'] <- 1
    beta$ai_value[beta$levels %in% input$ai_issue] <- 1
    beta$ai_value[beta$levels %in% input$ai_fin_trans] <- 1
    beta$ai_value[beta$levels %in% input$ai_account] <- 1
    beta$ai_value[beta$levels %in% input$ai_funding] <- 1
    beta$ai_value[beta$levels %in% input$ai_gov_relat] <- 1
  #Greenpeace
    beta$gp_value <- 0
    beta$gp_value[beta$levels == 'Greenpeace'] <- 1
    beta$gp_value[beta$levels %in% input$gp_issue] <- 1
    beta$gp_value[beta$levels %in% input$gp_fin_trans] <- 1
    beta$gp_value[beta$levels %in% input$gp_account] <- 1
    beta$gp_value[beta$levels %in% input$gp_funding] <- 1
    beta$gp_value[beta$levels %in% input$gp_gov_relat] <- 1
  #Oxfam
    beta$ox_value <- 0
    beta$ox_value[beta$levels == 'Oxfam'] <- 1
    beta$ox_value[beta$levels %in% input$ox_issue] <- 1
    beta$ox_value[beta$levels %in% input$ox_fin_trans] <- 1
    beta$ox_value[beta$levels %in% input$ox_account] <- 1
    beta$ox_value[beta$levels %in% input$ox_funding] <- 1
    beta$ox_value[beta$levels %in% input$ox_gov_relat] <- 1
  #Redcross
    beta$rc_value <- 0
    beta$rc_value[beta$levels == 'Red Cross'] <- 1
    beta$rc_value[beta$levels %in% input$rc_issue] <- 1
    beta$rc_value[beta$levels %in% input$rc_fin_trans] <- 1
    beta$rc_value[beta$levels %in% input$rc_account] <- 1
    beta$rc_value[beta$levels %in% input$rc_funding] <- 1
    beta$rc_value[beta$levels %in% input$rc_gov_relat] <- 1
    beta

@@

<!-- Persona Inputs {.sidebar} -->
<!-- ================================================= -->

@@

<!-- ```{r sidebar inputs, echo=FALSE} -->

<!-- # selectInput("model_choice",  -->
<!-- #             label = "Select Model:", -->
<!-- #             choices = c("public_political_social_charity_demo")) -->

<!-- selectInput("charity_importance",  -->
<!--           label = "Charity Importance:", -->
<!--           choices = c("0", '1', '2', '3','4','5','6','7')) -->

<!-- selectInput("trust_in_charity",  -->
<!--             label = "Charity Trust:", -->
<!--             choices = c("0", '1', '2', '3','4','5','6','7')) -->

<!-- selectInput("donation_frequency",  -->
<!--          label = "Donation Frequency:", -->
<!--          choices = c('Once a week',  -->
<!--                      'Once a Month', -->
<!--                      'Once every three months', -->
<!--                      'Once every six months',  -->
<!--                      'Once a year',  -->
<!--                      'Once every few years', -->
<!--                      'Never')) -->

<!-- selectInput("donation_amount",  -->
<!--          label = "Donation Amount:", -->
<!--          choices = c("$1-$49",  -->
<!--                      '$50-$99',  -->
<!--                      '$100-$499', -->
<!--                      '$500-$999', -->
<!--                      '$1,000-$4,999', -->
<!--                      '$5,000-$9,999', -->
<!--                      '$10,000+')) -->

<!-- selectInput("volunteer_12",  -->
<!--          label = "Volunteered in last 12 Months:", -->
<!--          choices = c("Yes", "No")) -->

<!-- selectInput("volunteer_frequency",  -->
<!--          label = "Volunteer Frequency:", -->
<!--          choices = c('Once a week', -->
<!--                      'Once a Month', -->
<!--                      'Once every three months',  -->
<!--                      'Once every six months',  -->
<!--                      'Once a year',  -->
<!--                      'Once every few years', -->
<!--                      'Never')) -->

<!-- selectInput("personal_activism",  -->
<!--          label = "Personal Activism:", -->
<!--          choices = c('Extremely involved', -->
<!--                      'Very involved',  -->
<!--                      'Moderately involved',  -->
<!--                      'Slightly involved', -->
<!--                      'Never involved')) -->

<!-- selectInput("family_activism",  -->
<!--          label = "Family Activism:", -->
<!--          choices = c('Extremely involved',  -->
<!--                      'Very involved',  -->
<!--                      'Moderately involved',  -->
<!--                      'Slightly involved', -->
<!--                      'Never involved')) -->

<!-- selectInput("religious_member",  -->
<!--          label = "Church Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("sport_member",  -->
<!--          label = "Sport or Recreational Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("art_member",  -->
<!--          label = "Art, Music, or Educational Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("labor_member",  -->
<!--          label = "Labor Union Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("political_member",  -->
<!--          label = "Political Party Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("environmental_member",  -->
<!--          label = "Enviornmental Org. Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("professional_member",  -->
<!--          label = "Professional Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("humanitarian_member",  -->
<!--          label = "Humanitarian Org. Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("consumer_member",  -->
<!--          label = "Consumer Org. Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("religious_member",  -->
<!--          label = "Church Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("other_member",  -->
<!--          label = "Other Org. Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("national_news",  -->
<!--          label = "Follow national news:", -->
<!--          choices = c('Multiple times a day',  -->
<!--                      'Every day',  -->
<!--                      "Once a week", -->
<!--                      "Hardly ever", -->
<!--                      "Never")) -->

<!-- selectInput("international_news",  -->
<!--          label = "Follow international news:", -->
<!--          choices = c('Always', -->
<!--                      "Sometimes", -->
<!--                      "Never")) -->

<!-- selectInput("news_medium",  -->
<!--          label = "Medium to follow news:", -->
<!--          choices = c('TV',  -->
<!--                      'Print',  -->
<!--                      "Online", -->
<!--                      "Social Media", -->
<!--                      "Radio", -->
<!--                      "Email newsletters", -->
<!--                      "News app")) -->

<!-- selectInput("international_news",  -->
<!--          label = "Follow international news:", -->
<!--          choices = c('Multiple times a day',  -->
<!--                      'Every day',  -->
<!--                      "Once a week", -->
<!--                      "Hardly ever", -->
<!--                      "Never")) -->

<!-- selectInput("follow_gov",  -->
<!--          label = "Follow government & public affairs:", -->
<!--          choices = c('Most of the time',  -->
<!--                      'Some of the time',  -->
<!--                      "Only now and then", -->
<!--                      "Hardly at all")) -->

<!-- selectInput("travel_developing",  -->
<!--          label = "Travel to developing country:", -->
<!--          choices = c('Yes', 'No')) -->

<!-- selectInput("polical_pref",  -->
<!--          label = "Polical views from liberal to conservative:", -->
<!--          choices = c("0", '1', '2', '3','4','5','6','7')) -->

<!-- selectInput("institution_trust",  -->
<!--          label = "Political institution trust from none to complete:", -->
<!--          choices = c("0", '1', '2', '3','4','5','6','7')) -->

<!-- selectInput("others_charitable",  -->
<!--          label = "People should be more charitable:", -->
<!--          choices = c("0", '1', '2', '3','4','5','6','7')) -->

<!-- selectInput("worship_attendance",  -->
<!--          label = "Worship service attendance:", -->
<!--          choices = c('Multiple times a week',  -->
<!--                      'Once a week',  -->
<!--                      "Once a month", -->
<!--                      "Once a year", -->
<!--                      "Never")) -->

<!-- selectInput("religion_importance",  -->
<!--          label = "Importance of religion:", -->
<!--          choices = c('Extremely important', -->
<!--                      'Very important', -->
<!--                      'Moderately important', -->
<!--                      'Slightly important', -->
<!--                      'Not at all important')) -->

<!-- selectInput("religion",  -->
<!--          label = "Religion:", -->
<!--          choices = c('Catholic', -->
<!--                      'Protestant', -->
<!--                      'Christian Orthodox', -->
<!--                      'Jewish', -->
<!--                      'Muslim', -->
<!--                      'Sikh', -->
<!--                      'Hindu', -->
<!--                      'Buddhist', -->
<!--                      'Atheist', -->
<!--                      'Other')) -->

<!-- selectInput("gender",  -->
<!--          label = "Gender:", -->
<!--          choices = c("Male", -->
<!--                      "Female", -->
<!--                      "Transgender", -->
<!--                      "Prefer not to say", -->
<!--                      "Other")) -->

<!-- selectInput("marital_status",  -->
<!--          label = "Marital Status:", -->
<!--          choices = c("Married", -->
<!--                      "Widowed", -->
<!--                      "Divorced", -->
<!--                      "Separated", -->
<!--                      "Never married")) -->

<!-- selectInput("education",  -->
<!--          label = "Education:", -->
<!--          choices = c("Less than high school", -->
<!--                      "High school", -->
<!--                      "Some college", -->
<!--                      "2 year degree", -->
<!--                      "4 year degree", -->
<!--                      "Graduate degree", -->
<!--                      "Doctorate")) -->

<!-- selectInput("income",  -->
<!--          label = "Income:", -->
<!--          choices = c('Less than $10,000',  -->
<!--                      '$10,000 to $19,999', -->
<!--                      '$20,000 to $29,999', -->
<!--                      '$30,000 to $39,999', -->
<!--                      '$40,000 to $49,999', -->
<!--                      '$50,000 to $59,999', -->
<!--                      '$60,000 to $69,999', -->
<!--                      '$70,000 to $79,999', -->
<!--                      '$80,000 to $89,999', -->
<!--                      '$90,000 to $99,999', -->
<!--                      '$100,000 to $149,999', -->
<!--                      '$150,000 to $199,999', -->
<!--                      '$200,000 to $299,999', -->
<!--                      '$300,000 or more')) -->

<!-- selectInput("race",  -->
<!--          label = "Race(s):", -->
<!--          choices = c('White', -->
<!--                      'Black or African American', -->
<!--                      'American Indian or Alaska Native', -->
<!--                      'Asian', -->
<!--                      'Native Hawaiian or Pacific Islander', -->
<!--                      'Other'),  -->
<!--          multiple = TRUE) -->

<!-- selectInput("education",  -->
<!--          label = "Education:", -->
<!--          choices = c("Less than high school", -->
<!--                      "High school", -->
<!--                      "Some college", -->
<!--                      "2 year degree", -->
<!--                      "4 year degree", -->
<!--                      "Graduate degree", -->
<!--                      "Doctorate")) -->

<!-- selectInput("age",  -->
<!--          label = "Age:", -->
<!--          choices = c('Under 18', -->
<!--                      '18 - 24', -->
<!--                      '25 - 34', -->
<!--                      '35 - 44', -->
<!--                      '45 - 54', -->
<!--                      '55 - 64', -->
<!--                      '65 - 74', -->
<!--                      '75 - 84', -->
<!--                      '85 or older')) -->

<!-- ``` -->

@@

Organization Breakdown {.tabset .tabset-fade}
--------------------------------------------------
### Amnesty International Market Share

@@

```{r valuebox ai}
renderValueBox({
  choice = df()

  persona = p_beta1 # Choose the persona

  valueBox(ai_rate,
           color = "#FFC30B",
           icon = "fa-percent")
})
```

```{r ai org inputs}
selectInput("ai_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

@@

  gauge(ai_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#FFC30B"),
        symbol = "%")
})
```

### Greenpeace Market Share

@@

```{r valuebox gp}
renderValueBox({
  choice = df()
  persona = p_beta1 # Choose the persona

  valueBox(gp_rate,
           color = "#3fad48",
           icon = "fa-percent")
})
```

@@

### Oxfam Market Share

@@

```{r valuebox ox}
renderValueBox({
  choice = df()

  persona = p_beta1 # Choose the persona

  valueBox(ox_rate,
           color = "#006633",
           icon = "fa-percent")
})
```

@@

### Redcross Market Share

@@

```{r valuebox rc}
renderValueBox({
  choice = df()

  persona = p_beta1 # Choose the persona

  valueBox(rc_rate,
           color = "#660000",
           icon = "fa-percent")
})
```

@@

>>>>

# Org Reactive Element
df <- reactive({
  #Amnesty International
    beta$ai_value <- 0
    beta$ai_value[beta$levels == 'Amnesty International'] <- 1
    beta$ai_value[beta$levels %in% input$ai_issue] <- 1
    beta$ai_value[beta$levels %in% input$ai_fin_trans] <- 1
    beta$ai_value[beta$levels %in% input$ai_account] <- 1
    beta$ai_value[beta$levels %in% input$ai_funding] <- 1
    beta$ai_value[beta$levels %in% input$ai_gov_relat] <- 1
  #Greenpeace
    beta$gp_value <- 0
    beta$gp_value[beta$levels == 'Greenpeace'] <- 1
    beta$gp_value[beta$levels %in% input$gp_issue] <- 1
    beta$gp_value[beta$levels %in% input$gp_fin_trans] <- 1
    beta$gp_value[beta$levels %in% input$gp_account] <- 1
    beta$gp_value[beta$levels %in% input$gp_funding] <- 1
    beta$gp_value[beta$levels %in% input$gp_gov_relat] <- 1
  #Oxfam
    beta$ox_value <- 0
    beta$ox_value[beta$levels == 'Oxfam'] <- 1
    beta$ox_value[beta$levels %in% input$ox_issue] <- 1
    beta$ox_value[beta$levels %in% input$ox_fin_trans] <- 1
    beta$ox_value[beta$levels %in% input$ox_account] <- 1
    beta$ox_value[beta$levels %in% input$ox_funding] <- 1
    beta$ox_value[beta$levels %in% input$ox_gov_relat] <- 1
  #Redcross
    beta$rc_value <- 0
    beta$rc_value[beta$levels == 'Red Cross'] <- 1
    beta$rc_value[beta$levels %in% input$rc_issue] <- 1
    beta$rc_value[beta$levels %in% input$rc_fin_trans] <- 1
    beta$rc_value[beta$levels %in% input$rc_account] <- 1
    beta$rc_value[beta$levels %in% input$rc_funding] <- 1
    beta$rc_value[beta$levels %in% input$rc_gov_relat] <- 1
    beta

})

# Persona Reactive Element
p <- reactive({
  #Amnesty International
    beta$p1_value <- 0
    beta$p1_value[beta$levels == 'Persona 1'] <- 1
    beta$p1_value[beta$levels %in% input$p1_charity_importance] <- 1
    beta$p1_value[beta$levels %in% input$p1_trust_in_charity] <- 1
    beta$p1_value[beta$levels %in% input$p1_donation_frequency] <- 1
    beta$p1_value[beta$levels %in% input$p1_donation_amount] <- 1
    beta$p1_value[beta$levels %in% input$p1_volunteer_12] <- 1
  #Greenpeace
    beta$p2_value <- 0
    beta$p2_value[beta$levels == 'Persona 2'] <- 1
    beta$p2_value[beta$levels %in% input$gp_issue] <- 1
    beta$p2_value[beta$levels %in% input$gp_fin_trans] <- 1
    beta$p2_value[beta$levels %in% input$gp_account] <- 1
    beta$p2_value[beta$levels %in% input$gp_funding] <- 1
    beta$p2_value[beta$levels %in% input$gp_gov_relat] <- 1
  #Oxfam
    beta$p3_value <- 0
    beta$p3_value[beta$levels == 'Persona 3'] <- 1
    beta$p3_value[beta$levels %in% input$ox_issue] <- 1
    beta$p3_value[beta$levels %in% input$ox_fin_trans] <- 1
    beta$p3_value[beta$levels %in% input$ox_account] <- 1
    beta$p3_value[beta$levels %in% input$ox_funding] <- 1
    beta$p3_value[beta$levels %in% input$ox_gov_relat] <- 1
    beta

@@

<!-- Persona Inputs  -->
<!-- ================================================= -->

@@

```{r sidebar inputs, echo=FALSE}

# # selectInput("model_choice",
# #             label = "Select Model:",
# #             choices = c("public_political_social_charity_demo"))
# 
# 
# selectInput("charity_importance",
#           label = "Charity Importance:",
#           choices = c("0", '1', '2', '3','4','5','6','7'))
# 
# 
# selectInput("trust_in_charity",
#             label = "Charity Trust:",
#             choices = c("0", '1', '2', '3','4','5','6','7'))
# 
# 
# 
# selectInput("donation_frequency",
#          label = "Donation Frequency:",
#          choices = c('Once a week',
#                      'Once a Month',
#                      'Once every three months',
#                      'Once every six months',
#                      'Once a year',
#                      'Once every few years',
#                      'Never'))
# 
# 
# 
# selectInput("donation_amount",
#          label = "Donation Amount:",
#          choices = c("$1-$49",
#                      '$50-$99',
#                      '$100-$499',
#                      '$500-$999',
#                      '$1,000-$4,999',
#                      '$5,000-$9,999',
#                      '$10,000+'))
# 
# 
# selectInput("volunteer_12",
#          label = "Volunteered in last 12 Months:",
#          choices = c("Yes", "No"))
# 
# 
# 
# selectInput("volunteer_frequency",
#          label = "Volunteer Frequency:",
#          choices = c('Once a week',
#                      'Once a Month',
#                      'Once every three months',
#                      'Once every six months',
#                      'Once a year',
#                      'Once every few years',
#                      'Never'))
# 
# 
# selectInput("personal_activism",
#          label = "Personal Activism:",
#          choices = c('Extremely involved',
#                      'Very involved',
#                      'Moderately involved',
#                      'Slightly involved',
#                      'Never involved'))
# 
# 
# selectInput("family_activism",
#          label = "Family Activism:",
#          choices = c('Extremely involved',
#                      'Very involved',
#                      'Moderately involved',
#                      'Slightly involved',
#                      'Never involved'))
# 
# 
# selectInput("religious_member",
#          label = "Church Membership:",
#          choices = c('Active Member',
#                      'Inactive Member',
#                      "Don't belong"))
# 
# 
# selectInput("sport_member",
#          label = "Sport or Recreational Membership:",
#          choices = c('Active Member',
#                      'Inactive Member',
#                      "Don't belong"))
# 
# 
# selectInput("art_member",
#          label = "Art, Music, or Educational Membership:",
#          choices = c('Active Member',
#                      'Inactive Member',
#                      "Don't belong"))
# 
# 
# selectInput("labor_member",
#          label = "Labor Union Membership:",
#          choices = c('Active Member',
#                      'Inactive Member',
#                      "Don't belong"))
# 
# 
# selectInput("political_member",
#          label = "Political Party Membership:",
#          choices = c('Active Member',
#                      'Inactive Member',
#                      "Don't belong"))
# 
# 
# selectInput("environmental_member",
#          label = "Enviornmental Org. Membership:",
#          choices = c('Active Member',
#                      'Inactive Member',
#                      "Don't belong"))
# 
# 
# selectInput("professional_member",
#          label = "Professional Membership:",
#          choices = c('Active Member',
#                      'Inactive Member',
#                      "Don't belong"))
# 
# 
# selectInput("humanitarian_member",
#          label = "Humanitarian Org. Membership:",
#          choices = c('Active Member',
#                      'Inactive Member',
#                      "Don't belong"))
# 
# 
# selectInput("consumer_member",
#          label = "Consumer Org. Membership:",
#          choices = c('Active Member',
#                      'Inactive Member',
#                      "Don't belong"))
# 
# 
# selectInput("religious_member",
#          label = "Church Membership:",
#          choices = c('Active Member',
#                      'Inactive Member',
#                      "Don't belong"))
# 
# 
# 
# 
# selectInput("other_member",
#          label = "Other Org. Membership:",
#          choices = c('Active Member',
#                      'Inactive Member',
#                      "Don't belong"))
# 
# 
# 
# selectInput("national_news",
#          label = "Follow national news:",
#          choices = c('Multiple times a day',
#                      'Every day',
#                      "Once a week",
#                      "Hardly ever",
#                      "Never"))
# 
# 
# selectInput("international_news",
#          label = "Follow international news:",
#          choices = c('Always',
#                      "Sometimes",
#                      "Never"))
# 
# 
# selectInput("news_medium",
#          label = "Medium to follow news:",
#          choices = c('TV',
#                      'Print',
#                      "Online",
#                      "Social Media",
#                      "Radio",
#                      "Email newsletters",
#                      "News app"))
# 
# 
# 
# selectInput("international_news",
#          label = "Follow international news:",
#          choices = c('Multiple times a day',
#                      'Every day',
#                      "Once a week",
#                      "Hardly ever",
#                      "Never"))
# 
# selectInput("follow_gov",
#          label = "Follow government & public affairs:",
#          choices = c('Most of the time',
#                      'Some of the time',
#                      "Only now and then",
#                      "Hardly at all"))
# 
# 
# selectInput("travel_developing",
#          label = "Travel to developing country:",
#          choices = c('Yes', 'No'))
# 
# 
# 
# selectInput("polical_pref",
#          label = "Polical views from liberal to conservative:",
#          choices = c("0", '1', '2', '3','4','5','6','7'))
# 
# 
# selectInput("institution_trust",
#          label = "Political institution trust from none to complete:",
#          choices = c("0", '1', '2', '3','4','5','6','7'))
# 
# 
# 
# selectInput("others_charitable",
#          label = "People should be more charitable:",
#          choices = c("0", '1', '2', '3','4','5','6','7'))
# 
# 
# selectInput("worship_attendance",
#          label = "Worship service attendance:",
#          choices = c('Multiple times a week',
#                      'Once a week',
#                      "Once a month",
#                      "Once a year",
#                      "Never"))
# 
# 
# selectInput("religion_importance",
#          label = "Importance of religion:",
#          choices = c('Extremely important',
#                      'Very important',
#                      'Moderately important',
#                      'Slightly important',
#                      'Not at all important'))
# 
# 
# selectInput("religion",
#          label = "Religion:",
#          choices = c('Catholic',
#                      'Protestant',
#                      'Christian Orthodox',
#                      'Jewish',
#                      'Muslim',
#                      'Sikh',
#                      'Hindu',
#                      'Buddhist',
#                      'Atheist',
#                      'Other'))
# 
# 
# selectInput("gender",
#          label = "Gender:",
#          choices = c("Male",
#                      "Female",
#                      "Transgender",
#                      "Prefer not to say",
#                      "Other"))
# 
# 
# selectInput("marital_status",
#          label = "Marital Status:",
#          choices = c("Married",
#                      "Widowed",
#                      "Divorced",
#                      "Separated",
#                      "Never married"))
# 
# 
# selectInput("education",
#          label = "Education:",
#          choices = c("Less than high school",
#                      "High school",
#                      "Some college",
#                      "2 year degree",
#                      "4 year degree",
#                      "Graduate degree",
#                      "Doctorate"))
# 
# selectInput("income",
#          label = "Income:",
#          choices = c('Less than $10,000',
#                      '$10,000 to $19,999',
#                      '$20,000 to $29,999',
#                      '$30,000 to $39,999',
#                      '$40,000 to $49,999',
#                      '$50,000 to $59,999',
#                      '$60,000 to $69,999',
#                      '$70,000 to $79,999',
#                      '$80,000 to $89,999',
#                      '$90,000 to $99,999',
#                      '$100,000 to $149,999',
#                      '$150,000 to $199,999',
#                      '$200,000 to $299,999',
#                      '$300,000 or more'))
# 
# 
# 
# selectInput("race",
#          label = "Race(s):",
#          choices = c('White',
#                      'Black or African American',
#                      'American Indian or Alaska Native',
#                      'Asian',
#                      'Native Hawaiian or Pacific Islander',
#                      'Other'),
#          multiple = TRUE)
# 
# 
# selectInput("education",
#          label = "Education:",
#          choices = c("Less than high school",
#                      "High school",
#                      "Some college",
#                      "2 year degree",
#                      "4 year degree",
#                      "Graduate degree",
#                      "Doctorate"))
# 
# 
# selectInput("age",
#          label = "Age:",
#          choices = c('Under 18',
#                      '18 - 24',
#                      '25 - 34',
#                      '35 - 44',
#                      '45 - 54',
#                      '55 - 64',
#                      '65 - 74',
#                      '75 - 84',
#                      '85 or older'))

@@

Organization Breakdown {.tabset .tabset-fade}
--------------------------------------------------
### Org 1

@@

```{r valuebox ai commented}
# renderValueBox({
#   choice = df()
#   
#   persona = p_beta1 # Choose the persona
#   
#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
#   
#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
#   
#   valueBox(ai_rate,
#            color = "#FFC30B",
#            icon = "fa-percent")
# })
```

```{r ai org inputs}

# Some kind of Org Id that could select the organization you are looking at? Not sure how to make it change the label in the graph
selectInput("org_id",
            label = "Select Organization:",
            choices = c("Amnesity International",
                        "Green Peace",
                        "Oxfam",
                        "Red Cross"))

selectInput("ai_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

@@

  gauge(ai_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#FFC30B"),
        symbol = "%")
})

renderGauge({
  choice = df()
  persona = p_beta2 # Choose the persona

  gauge(ai_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#3fad48"),
        symbol = "%")
})

renderGauge({
  choice = df()
  persona = p_beta3 # Choose the persona

  gauge(ai_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#006633"),
        symbol = "%")
})
```

### Org 2

@@

```{r valuebox gp commented}
# renderValueBox({
#   choice = df()
#   persona = p_beta1 # Choose the persona
#   
#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
#   
#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
#   
#   valueBox(gp_rate,
#            color = "#3fad48",
#            icon = "fa-percent")
# })
```

@@

### Org 3

@@

```{r valuebox ox commented}
# renderValueBox({
#   choice = df()
#   
#   persona = p_beta1 # Choose the persona
#   
#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
#   
#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
#   
#   valueBox(ox_rate,
#            color = "#006633",
#            icon = "fa-percent")
# })
```

@@

### Org 4

@@

```{r valuebox rc commented}
# renderValueBox({
#   choice = df()
#   
#   persona = p_beta1 # Choose the persona
#    
#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
#   
#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
#   
#   valueBox(rc_rate,
#            color = "#660000",
#            icon = "fa-percent")
# })
```

@@

### Persona 1

```{r persona 1 inputs}

# selectInput("model_choice",
#             label = "Select Model:",
#             choices = c("public_political_social_charity_demo"))

selectInput("charity_importance",
          label = "Charity Importance:",
          choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("trust_in_charity",
            label = "Charity Trust:",
            choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("donation_frequency",
         label = "Donation Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months',
                     'Once every six months',
                     'Once a year',
                     'Once every few years',
                     'Never'))

selectInput("donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'))

selectInput("volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("Yes", "No"))

selectInput("volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months',
                     'Once every six months',
                     'Once a year',
                     'Once every few years',
                     'Never'))

selectInput("personal_activism",
         label = "Personal Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

selectInput("family_activism",
         label = "Family Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

selectInput("religious_member",
         label = "Church Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("sport_member",
         label = "Sport or Recreational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("labor_member",
         label = "Labor Union Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("political_member",
         label = "Political Party Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("environmental_member",
         label = "Enviornmental Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("professional_member",
         label = "Professional Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("consumer_member",
         label = "Consumer Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("other_member",
         label = "Other Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("national_news",
         label = "Follow national news:",
         choices = c('Multiple times a day',
                     'Every day',
                     "Once a week",
                     "Hardly ever",
                     "Never"))

selectInput("international_news",
         label = "Follow international news:",
         choices = c('Always',
                     "Sometimes",
                     "Never"))

selectInput("news_medium",
         label = "Medium to follow news:",
         choices = c('TV',
                     'Print',
                     "Online",
                     "Social Media",
                     "Radio",
                     "Email newsletters",
                     "News app"))

selectInput("international_news",
         label = "Follow international news:",
         choices = c('Multiple times a day',
                     'Every day',
                     "Once a week",
                     "Hardly ever",
                     "Never"))

selectInput("follow_gov",
         label = "Follow government & public affairs:",
         choices = c('Most of the time',
                     'Some of the time',
                     "Only now and then",
                     "Hardly at all"))

selectInput("travel_developing",
         label = "Travel to developing country:",
         choices = c('Yes', 'No'))

selectInput("political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("others_charitable",
         label = "People should be more charitable:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("worship_attendance",
         label = "Worship service attendance:",
         choices = c('Multiple times a week',
                     'Once a week',
                     "Once a month",
                     "Once a year",
                     "Never"))

selectInput("religion_importance",
         label = "Importance of religion:",
         choices = c('Extremely important',
                     'Very important',
                     'Moderately important',
                     'Slightly important',
                     'Not at all important'))

selectInput("religion",
         label = "Religion:",
         choices = c('Catholic',
                     'Protestant',
                     'Christian Orthodox',
                     'Jewish',
                     'Muslim',
                     'Sikh',
                     'Hindu',
                     'Buddhist',
                     'Atheist',
                     'Other'))

selectInput("gender",
         label = "Gender:",
         choices = c("Male",
                     "Female",
                     "Transgender",
                     "Prefer not to say",
                     "Other"))

selectInput("marital_status",
         label = "Marital Status:",
         choices = c("Married",
                     "Widowed",
                     "Divorced",
                     "Separated",
                     "Never married"))

selectInput("education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate degree",
                     "Doctorate"))
